A quantitative framework for investigating the reliability of network construction

### 2018-03-08 manuscript/CI_interactions.tex
finished read-through of main text

% Main text can be up to 7500 words, 10 fig., tables, boxes

@@

  % Can be up to 200 words. This is 200 exactly.
  % Word count can be up to 7500, we're at about 5700 without the boxes. Should be grand.

@@

\linenumbers
\begin{spacing}{2.0}
\section*{Introduction}

@@

    Beyond ``true" variation in network structure, several researchers have pointed to the importance of sampling intensity for the assessment of network structure (e.g.,~\citealp{Martinez1999,Bluthgen2006,Bluthgen2007}). An assessment of the accumulation of interactions with increasing sampling effort suggests that it is even more challenging to document interactions than species~\citep{Poisot2012}. As a result, it has been proposed that interactions should be described probabilistically and network metrics computed accordingly~\citep{Poisot2016}. Yet, to date, we lack the quantitative methodology to deal with the uncertainty generated by spatiotemporal variation in ecological interactions and by sampling. Even in extremely well-sampled networks, uneven sampling across species (or pairs of species) can lead to the erroneous inference that some species do not interact because they co-occur rarely or have not yet been observed together - even if they do interact when they do co-occur (see Box 1 for an example). Nearly all network studies will thus neglect some interactions, necessitating an approach that acknowledges this uncertainty.

    In this study, we formalize the description of interactions between species as probabilities and develop analytical tools to capture the uncertainty in the estimation of pairwise interactions. We focus on binary interactions as a first step, but the framework could be expanded to deal with interaction frequencies and strength. To define the problem, we first identify the different contributions to the uncertainty of an interaction and discuss the implications of each source of uncertainty for the properties of ecological networks. Next, we develop an analytical framework to quantify the uncertainty around interactions in an empirical web. We illustrate this framework using the most extensively sampled network to date (Box 1).  Finally, we offer tangible recommendations for improved descriptors of ecological interactions [[double-check that we do this]]. Through these efforts, we demonstrate both the utility of our approach and the importance of acknowledging the uncertainty inherent in network studies.

@@

  To define the problems associated with quantifying ecological interaction networks, we will start from the perspective of an empirical community ecologist faced with the task of describing a previously unknown interaction network. This ecologist will be interested in generating a description of the species/nodes present, and the links between them~\citep{Roslin2016}.  Importantly, the information sought is conveyed by both the presence and \emph{absence} of links. The two types of information are not, however, equally certain. An observed link will always remain an observed link, but there are multiple reasons why a given link may not be observed. Thus, the detection of any interaction is a stochastic process. We define three nested levels of uncertainty contributing to this stochasticity:

@@

    First, and most fundamentally, we do not know whether or not a pair of species have the appropriate characteristics (or traits) to interact. We define the probability of an interaction $L$ given those characteristics $\mathbf{T}$ as $P(L | \mathbf{T})=\lambda$. Obviously, if $k$ (the number of observed interactions) is 0, it is possible that the two species could not interact even if there were no external constraints (e.g., temporal or environmental separation) preventing the interaction from occurring. As a simple example, a prey species may be too large to be consumed by a particular predator. In such cases, $\lambda$ would take a value of 0 and there would be no uncertainty. 
    Nevertheless, it is also possible that the interaction is a rare phenomenon with $\lambda>0$ that has not yet been documented. This source of uncertainty is the one documented by trait-matching models~\citep{Bartomeus2016}. It arises because every model is imperfect and lacks information (i.e. about traits) that could be used to define constraints on the interaction. In other words, with sufficient sampling and all information accessible, this interaction probability $\lambda$ should either tend to 0 or to 1 and the uncertainty should vanish.

@@

    Even when an interaction is feasible, i.e. $L=1$, it may not occur at a given location or moment in time because of local constraints such as inclement weather or the lack of suitable habitat. We define the realisation of the interaction process with the variable $X$, given that the interaction is feasible, as a stochastic process with associated probability $P(X|L=1)=\chi$. This phenomenon of interaction contingencies is usually not considered in network studies, but there is a rich literature in community ecology about the contingencies of interactions. Phenological matching~\citep{MillerRushing2010,Gezon2016}, species preferences~\citep{Pires2011,Novak2015,Coux2016}, and fear effects of other species~\citep{Luttbeg2005,Wirsing2008} are just some of the factors contributing to variation in the frequency of interactions between a given pair of species.
    % We imagine for instance that an interaction between a gall and a parasitoid might not be recorded at a location because it was the wrong time of the year and the gall had not yet formed (phenological constraints), a late frost killed the larvae (an abiotic environmental constraint), another parasitoid species competitively excluded the parasitoid species of interest (a biotic environmental constraint) or simply the parasitoid is too rare to interact with all of its viable hosts (an abundance constraint).

@@

    Lastly, measurement errors are a pervasive source of uncertainty in the observation of ecological processes. Given that an interaction with the variable $D$, given an interaction is feasible and occurs under the local conditions, we may define the detection of an interaction, $D$, as a stochastic process with the associated probability $P(D|X=1,L=1)=\delta$. Detection failure could happen for several reasons, for instance if the rearing of a parasitoid fails with inappropriate lab conditions, because of species mis-identification, or because the interaction is very rare (see~\citet{Wirta2014} for examples of some of these difficulties and partial solutions to them). Some sources of detection error can be minimised with appropriate sampling effort ($\delta$ will converge to one with increasing number of samples), but other sources are often difficult to reduce (e.g. the occurrence of cryptic species might require molecular analysis for appropriate taxonomic identification as in~\citealt{Wirta2014,Frost2016}).

@@

    Together, the combination of these three sources of uncertainty --interaction uncertainty, process uncertainty, and detection uncertainty-- results in a range of potential explanations for the observation of an absence of interaction ($D$, $X$, and/or $L = 0$). The ecologist wanting to describe the network, however, is specifically interested in the situation where $L = 0$ (i.e., in true absences). Thus, while there is have no difficulty interpreting the observation of an interaction, the observation of an absence of an interaction offers more of a challenge since it must be decomposed into different quantities. It is particularly important to rule out the situations where $D=0 \cup X = 1 \cup L=1$, i.e. where the interaction occurred at the location but was not observed, and $D=1 \cup X = 0 \cup L =1$, when the interaction is feasible and would have been detected but did not occur at the local site. The occurrence of a true absence, our quantity of interest, corresponds to the joint event $L=0 \cup X=1 \cup D=1$, but in reality an empirical ecologist will measure the marginal probability $P(L) = k/n$ where $k$ is again the number of observed interactions and $n$ the number of observed co-occurrences.

    The considerations above raise a major challenge: when faced with empirical data, how may we infer whether unobserved interactions went undetected due to sampling or whether they truly do not occur? How then may we refine our sampling approaches to reduce uncertainties, and do we gain insights into the impact of multiple processes on field observations? Importantly, some sources of uncertainty can be minimised with appropriate sampling design and efforts while other sources are difficult or impossible to reduce since they are generated by chance variation created by the very process in which we are interested.

@@

  [[Tomas suggests removing the following because it slows down proceedings, Anna and Dom want it back. Shortening sounds like a good middle ground:]]
  The basic information that we are collecting consists of matrices of interaction partners. Our count of interactions between two species reflects uncertainty with respect to whether two species are capable of interacting when co-occurring at a given site ($\lambda$), chance variation in whether the interaction is realised ($\chi$),  and uncertainty with respect to whether it is detected when realised ($\delta$). In this case, what can we do to pin down any of these different types of variation?

  The obvious rule of thumb is to ``sample more" (see Fig.~\ref{upper_limits} for a demonstration of the power of increasing sample size), but we note that there are limits to the utility of this motto. Sampling more will clearly reduce uncertainty regarding the upper bound of the probability of interaction, and it will also increase the probability of detecting unlikely interactions (i.e. interactions occurring with a low probability). Yet, since the probability of observing the co-occurrence of two species will always be higher than the probability of observing their interaction (since the probability of interaction is conditional on both interaction partners being present; see Fig.~\ref{histograms}E-F), we will accumulate observations of co-occurrences faster than we will accumulate observations of interactions. Thus, the more we sample, the more zeros will appear in our interaction matrix, which may seem like a counter-intuitive outcome.

  As a solution towards deciding whether unobserved interactions were undetected due to sampling, or whether they truly do not occur,~\citet{Weinstein2017} used repeated sampling rounds to estimate the daily probability of detecting a hummingbird interaction, and to thereby model the observation and process mechanisms. While conceptually attractive, this approach is unsuitable for interactions occurring over longer time scales (e.g., associations between hosts and parasitoids with a single generation per year), or very rare interactions which might not occur on any of the sampling days or might involve individuals of a species that are not under observation. What is worse, the problem persists that if a given interaction is not observed on a given day, this could be either because it was impossible that day despite being otherwise feasible [$P(X|D=1,L=1)=0$], because interaction between the two did occur but could not be observed [$P(D|X=1,L=1)=0$], or from any combination of the two. From a conceptual perspective, this approach will thus fail to satisfactorily distinguish between sources of uncertainty. Most importantly, if two species are never observed co-occurring during several days of sampling then we have learned nothing about their probability of interacting if they should ever co-occur. In other words, there is no information about interactions without co-occurrence.

  An added complication is that not all sources of uncertainty are proportional to sample size. To record an interaction between A and B, we need to identify both partners correctly (a non-trivial problem in many food webs; e.g.~\citealp{Kaartinen2011,Roslin2016}) and be able to resolve all interactions with a similar likelihood. For both molecular and rearing techniques, certain types of interactions may go unnoticed due to technical challenges~\citep{Wirta2014}. This can bias the set of recorded interactions. The bottom line is that separating different sources of uncertainty is difficult indeed. As an alternative to abandoning empirical networks or continuing to ignore the uncertainty inherent in undetected observations, we propose that some insight regarding the detectability of interactions between species not found co-occurring may be gained from data on other species between which interactions are known to be feasible.

\section*{A naive quantification of interaction probability and uncertainty}

@@

   [[Move this paragraph to intro?]] It is getting more and more common to represent interactions as probabilities in theoretical models of network structure. For example, the minimum potential model introduces gaps in the feeding niche of predators by sampling based on the likelihood of each interaction~\citep{Allesina2008}, while a Gaussian probability function is used to represent the niche by~\citet{Williams2010}. \citet{Eklof2013} also introduced variability  in the computation of network dimensions, allowing the absence of interactions within the n-dimension niche of every species. Empirical investigation of trait-matching constraints often consider the occurrence of interactions as binomial process (e.g.,~\citealp{Rohr2016}). There are also ways to perform analysis of probabilistic networks, with almost all metrics having a probabilistic version~\citep{Poisot2016}. But there is not yet consensus on what an interaction probability between a pair of species means, and this is definitely a problem when comes time to estimate the uncertainty of both pairwise interactions and entire networks.

@@

  The variance of a Bernoulli experiment is $n\lambda$(1-$\lambda$). It is important to remember that this variance describes the variability of the number of successes $k$ for $n$ trials and is not the variance associated with the estimation of $\lambda$. Given this variance, it is possible to compute the confidence interval for the MLE of $\lambda$ using any of several methods, including the \emph{Wilson score interval}, the \emph{Clopper-Pearson interval}, and the \emph{Agresti-Coull interval} (for details, see [\citealp{Brown2001}]). Finding this estimate is therefore quite straightforward, but it nonetheless has two drawbacks. First, $\lambda$ is not a single point estimate but rather a random variable with a given uncertainty, the distribution of which is unknown. This means that even if $k = 0$ in a given sample, this does not necessarily imply that the two species will never interact. Rather, $k = 0$ implies that `no interaction' is the most likely outcome when the species do co-occur but there is nonetheless a substantial chance that the two species \emph{could} interact. In the situation where $k>0$, in contrast, we are sure that the interaction is feasible ($L = 1$) but still cannot be sure of the cause if the interaction is not observed at some sites/times (i.e., we cannot say why $k<n$). There may be local constraints ($X=0$) or we might simply not observe the interaction in every sample ($D<1$).

@@

          The ecological network literature boasts a solid collection of networks for which connectance has been calculated and for which we can thus define the connectance distribution. Connectance is measured as $C = L/S^2$, where $L$ is the number of interactions and $S$ is the number of species. It measures the filling of an interaction matrix and thereby expresses the average probability that any two species interact with each other. If we know only the mean $\overline{C}$ and the variance $\sigma_C^2$ of the distribution of $C$,
          % [[from the literature or from our network? Has to be from the literature - if it was our network we'd know way more than just C]] 
          then the beta parameters could be computed as follows using the method of moments:

@@

          The degree of a node in a network is defined as its number of connections to other nodes. The degree distribution of a network is then the probability distribution of these degrees over the whole network and the standardised degree could therefore be interpreted as an interaction probability. It is consequently possible to use the degree distribution to inform the prior distribution. The degree distribution could come from several networks, from a similar network (e.g. a known network at slightly different location) or from the network of interest if interaction probabilities for some species are already documented. The latter approach allows to apply information from known, abundant species to the rarest species for which interactions are less frequently documented.

          If our focal network describes a system similar to that in a known network, we can use the distribution of interaction probabilities in that network to inform our prior. The probability of any interaction $L_{ij}$ depends on the degrees of species $i$ and $j$. Using normalised degrees $\Delta_i$ and $\Delta_j$ (i.e., degrees divided by the number of species in the network), we can obtain the probability of interaction $L_{ij}$=$\Delta_i\times\Delta_j$. Similar to the procedure for degree distribution, the distribution of these interaction probabilities derived from a similar network or a suite of networks can be used to establish a prior distribution before any data from the focal network are collected. For distributions of either degrees or interaction probabilities, the procedure for the estimation of the hyper parameters follows the same approach as described above for connectance except that each measurement is at the individual interaction level instead of the network level.

@@

          As a fourth and final approach to obtain the prior distribution of $\lambda$, we envisage using the outcome of a trait-matching model, provided such a model has been documented using external data and relevant traits are available. In such as case, the prior distribution would follow the function $P(\lambda|\mathbf{T})=f(\mathbf{T})$ based on a set of traits for both species $\mathbf{T}$. There are several techniques available to perform this inference of interaction probability, some of which are Bayesian, and we refer to~\citet{Bartomeus2016} and~\citet{Weinstein2017} for recent reviews about this topic. Note that in this case the prior might not be beta-distributed and numerical methods might be required to compute the posterior distribution.

@@

  The Bayesian framework can be illustrated with a simple quantitative example. Suppose we have $n = 10$ observations of co-occurrence between species $i$ and species $j$ in a given time interval and area, and $k = 3$ observations of interactions. The maximum likelihood estimate of the interaction probability (Box~\ref{box2}) is simply $\lambda_{MLE} = 3/10 = 0.3$.

@@

\section*{Scaling up uncertainty from pairwise interactions to networks}

    %It is fairly straightforward to compute most of network metrics when the different $\lambda$ of the adjacency matrix are known, without variance~\citep{Poisot2016}. Several of these metrics derive directly from quantitative indices of network structure which are equivalent to $\lambda$. The remainder, originally defined for binary networks, can be adjusted to account for interaction probabilities between zero and one. It is not as easy, however, to understand how the uncertainty in these estimated interaction probabilities influences network metrics. Computation of these metrics involves non-linear functions. Since Jensen's inequality states that the average of a non-linear function of a stochastic variable differs from the function of the average of that variable, any uncertainty in the values of $\lambda$ could bias both the mean and variance of a network metric. For instance, assume that among the pairs of species with few observed co-occurrences there are many pairs which truly interact. If we %begin with no observed links for these pairs, then correcting for these false absences will inflate the number of links and consequently influence metrics such as connectance, nestedness, and degree distribution. While we can, as described above, calculate these network metrics using fixed estimates for $\lambda$, no analytical solution currently exists for uncertain $\lambda$. Instead we must rely on computer simulations. 
    In the following section, we will provide an empirical example based on the well-sampled system of \emph{Salix}  plants, herbivorous gallers, and their natural enemies described by~\citet{Kopelke2017}; see Box~\ref{box1} or \emph{Appendix S2} for a description). 
    %This tripartite network can be examined as two bipartite networks, namely \emph{Salix}-galler and galler-natural enemy networks. 
    We will show how the uncertainty arising from both absences of co-occurrences and false absences of interactions impact these metrics. %We find uncertainty influences both the average and the variance of network metrics, putting in perspective traditional network comparison studies where these metrics are assumed to be fixed entities.

@@

      In a strict Bayesian framework, we wish to use a prior distribution that does not rely on any information from the study at hand. Network data for a similar study system may, however, not be available. In that case, one might use the first sub-network collected as ``training data" to guide future sampling. To simulate this situation, we created priors using a single sub-network from the middle of the geographical distribution of the~\citep{Kopelke2017} dataset (Zillis sub-network). To demonstrate how the use of a data from a different system can affect the prior distribution and conclusions based on it, we repeated our analyses using priors derived from a much smaller \emph{Salix}-galler-natural enemy system~\citep{Barbour2016,Barbour2016Dryad}. This smaller system was much more densely-connected than that described in~\citet{Kopelke2017} and provided unreasonable distributions for interaction probabilities (\emph{Appendix S4}).

@@

  \subsection*{How many samples are required to reach a minimal precision}

>>>>

\clearpage
% Main text can be up to 7500 words, 10 fig., tables, boxes

@@

  % Can be up to 200 words. This is 200 exactly.
  % Word count can be up to 7500, we're at about 6506 without the boxes, intro, references.

@@

% AC: Good idea - I've also changed the "In this study, we ..." paragraph to make it sound less like we just built some software and hopefully emphasise the conceptual side more.

\linenumbers
\clearpage

\begin{spacing}{2.0}
\section*{Introduction}

@@

    Beyond ``true" variation in network structure, several researchers have pointed to the importance of sampling intensity for the assessment of network structure (e.g.,~\citealp{Martinez1999,Bluthgen2006,Bluthgen2007}). An assessment of the accumulation of interactions with increasing sampling effort suggests that it is even more challenging to document interactions than species~\citep{Poisot2012}. As a result, it has been proposed that interactions should be described probabilistically and network metrics computed accordingly~\citep{Poisot2016}. Early work in this vein includes food-web models using likelihood-based approaches~\citep{Allesina2008} or Gaussian~\citep{Williams2010} or binomial~\citep{Rohr2016} probability functions for each possible interaction. These models may include information about species' traits~\citep{Rohr2016} or may attempt to reproduce empirical network structures using a set of simple rules~\citep{Allesina2008,Williams2010}.
    % \citet{Eklof2013} also introduced variability  in the computation of network dimensions, allowing the absence of interactions within the n-dimension niche of every species. % AC: Does this really fit in now that this is in the introduction?

    Despite these preliminary efforts, to date we lack the quantitative methodology to deal with the uncertainty generated by spatiotemporal variation in ecological interactions and by sampling. Even in extremely well-sampled networks, uneven sampling across species (or pairs of species) can lead to the erroneous inference that some species do not interact because they co-occur rarely or have not yet been observed together - even if they do interact when they do co-occur (see Box 1 for an example). Nearly all network studies will thus neglect some interactions, necessitating an approach that acknowledges this uncertainty.

   % [[Move this paragraph to intro?]] It is getting more and more common to represent interactions as probabilities in theoretical models of network structure. For example, the minimum potential model introduces gaps in the feeding niche of predators by sampling based on the likelihood of each interaction~\citep{Allesina2008}, while a Gaussian probability function is used to represent the niche by~\citet{Williams2010}. \citet{Eklof2013} also introduced variability  in the computation of network dimensions, allowing the absence of interactions within the n-dimension niche of every species. Empirical investigation of trait-matching constraints often consider the occurrence of interactions as binomial process (e.g.,~\citealp{Rohr2016}). There are also ways to perform analysis of probabilistic networks, with almost all metrics having a probabilistic version~\citep{Poisot2016}. But there is not yet consensus on what an interaction probability between a pair of species means, and this is definitely a problem when comes time to estimate the uncertainty of both pairwise interactions and entire networks.

    In this study, we formalize the description of interactions between species as probabilities and develop analytical tools to capture the uncertainty in the estimation of these interactions. We focus on binary interactions as a first step, but the framework could be expanded to deal with interaction frequencies and strength. To define the problem, we first identify the different contributions to the uncertainty of an interaction and discuss the implications of each source of uncertainty for the properties of ecological networks. Next, we develop an analytical framework to quantify the uncertainty around interactions in an empirical web. We illustrate this framework using the most extensively sampled network to date (Box 1).  Finally, we offer tangible recommendations for improved descriptors of ecological interactions [[double-check that we do this]]. Through these efforts, we demonstrate both the utility of our approach and the importance of acknowledging the uncertainty inherent in network studies.

@@

  To define the problems associated with quantifying ecological interaction networks, we will start from the perspective of an empirical community ecologist faced with the task of describing a previously unknown interaction network. This ecologist will be interested in generating a description of the species/nodes present and the links between them~\citep{Roslin2016}.  Importantly, the information sought is conveyed by both the presence and \emph{absence} of links. Presences and absences are not, however, equally certain. An observed link will always remain an observed link, but there are multiple reasons why a given link may not be observed. Thus, the detection of any interaction is a stochastic process. We define three nested levels of uncertainty contributing to this stochasticity: interaction uncertainty, process uncertainty, and detection uncertainty.

@@

      First, and most fundamentally, we do not know whether or not a pair of species have the appropriate characteristics (or traits) to interact. We define the probability of an interaction $L$ given those characteristics $\mathbf{T}$ as $P(L | \mathbf{T})=\lambda$. Obviously, if $k$ (the number of observed interactions) is 0, it is possible that the two species would not interact even if there were no external constraints (e.g., temporal or environmental separation) preventing the interaction from co-occurring. As a simple example, a prey species may be too large to be consumed by a particular predator. In such cases, $\lambda$ would take a value of 0 and there would be no uncertainty.

      Nevertheless, it is also possible that the interaction is a rare phenomenon with $\lambda>0$ that has not yet been documented. This source of uncertainty is the one documented by trait-matching models~\citep{Bartomeus2016}. It arises because every model is imperfect and lacks information (i.e. about traits) that could be used to define constraints on the interaction~\citep{Dormann2017}. Further study may, however, eventually reveal the traits of interest and allow us to reduce interaction uncertainty. In other words, with sufficient sampling and all information accessible, this interaction probability $\lambda$ should either tend to 0 or to 1.

@@

     Even when an interaction is feasible, i.e. $L=1$, it may not occur at a given location or moment in time because of local constraints such as inclement weather or the lack of suitable habitat. We define the realisation of the interaction process with the variable $X$, given that the interaction is feasible, as a stochastic process with associated probability $P(X|L=1)=\chi$. This phenomenon of interaction contingencies is usually not considered in network studies, but there is a rich literature in community ecology about the contingencies of interactions. Phenological matching~\citep{MillerRushing2010,Gezon2016}, species preferences~\citep{Pires2011,Novak2015,Coux2016}, and fear effects of other species~\citep{Luttbeg2005,Wirsing2008} are just some of the factors contributing to variation in the frequency of interactions between a given pair of species. Although some of the factors leading to process uncertainty can be addressed in mesocosm studies of networks (e.g., environmental conditions can be held stable), process uncertainty is likely inevitable in the field. 
      % We imagine for instance that an interaction between a gall and a parasitoid might not be recorded at a location because it was the wrong time of the year and the gall had not yet formed (phenological constraints), a late frost killed the larvae (an abiotic environmental constraint), another parasitoid species competitively excluded the parasitoid species of interest (a biotic environmental constraint) or simply the parasitoid is too rare to interact with all of its viable hosts (an abundance constraint).

@@

      Lastly, measurement errors are a pervasive source of uncertainty in the observation of ecological processes. Given that an interaction is feasible and occurs under the local conditions ($L$=1 and $X$=1), we may define the detection of an interaction, $D$, as a stochastic process with the associated probability $P(D|X=1,L=1)=\delta$. Detection failure could happen for several reasons including failure to rear a parasitoid, species mis-identification, or because the interaction is very rare (see~\citet{Wirta2014} for examples of some of these difficulties and partial solutions to them). Some sources of detection error can be minimised with appropriate sampling effort ($\delta$ will converge to one with increasing number of samples), but other sources are often difficult to reduce (e.g. the occurrence of cryptic species might require molecular analysis for appropriate taxonomic identification as in~\citealt{Wirta2014,Frost2016}).

@@

    Together, the combination of these three sources of uncertainty --interaction uncertainty, process uncertainty, and detection uncertainty-- results in a range of potential explanations for the observation of an absence of interaction ($D$, $X$, and/or $L = 0$). The ecologist wanting to describe the network, however, is specifically interested in the situation where $L = 0$ (i.e., in true absences). Thus while there is no difficulty interpreting the observation of an interaction, the observation of an absence of an interaction offers more of a challenge since it must be decomposed into different quantities. It is particularly important to rule out the situations where $D=0 \cup X = 1 \cup L=1$, i.e. where the interaction occurred at the location but was not observed, and $D=1 \cup X = 0 \cup L =1$, i.e., where the interaction is feasible and would have been detected but did not occur at the local site. The occurrence of a true absence, our quantity of interest, corresponds to the joint event $L=0 \cup X=1 \cup D=1$ but in reality an empirical ecologist will measure the marginal probability $P(L) = k/n$ where $k$ is again the number of observed interactions and $n$ the number of observed co-occurrences.

    The considerations above raise a major challenge: when faced with empirical data, how may we infer whether unobserved interactions went undetected due to sampling or whether they truly do not occur? How then may we refine our sampling approaches to reduce uncertainties, and do we gain insights into the impact of multiple processes on field observations? Importantly, some sources of uncertainty can be minimised with appropriate sampling design and efforts while other sources are difficult or impossible to reduce since they are generated by chance variation created by the very process in which we are interested. Given this multifaceted problem of uncertainty, what can we do to separate the different types of variation and reduce those that can be reduced?

@@

    %AC: I've added this section back in but shortened it slightly (mostly the first paragraph). We're ok on word-count with this included.

    % The basic information that we are collecting consists of matrices of interaction partners. Our count of interactions between two species reflects uncertainty with respect to whether two species are capable of interacting when co-occurring at a given site ($\lambda$), chance variation in whether the interaction is realised ($\chi$),  and uncertainty with respect to whether it is detected when realised ($\delta$). In this case, what can we do to pin down any of these different types of variation?

    The obvious rule of thumb is to ``sample more" (see Fig.~\ref{upper_limits} for a demonstration of the power of increasing sample size). Sampling more will clearly reduce uncertainty regarding the upper bound of the probability of interaction and it will also increase the probability of detecting unlikely interactions (e.g.,. interactions where $L$=1 but process uncertainty is high).
    Despite these benefits, we note that there are limits to the utility of increased sampling. Since the probability of observing the co-occurrence of two species will always be higher than the probability of observing their interaction (since the probability of interaction is conditional on both interaction partners being present; see Fig.~\ref{histograms}E-F), we will accumulate observations of co-occurrences faster than we will accumulate observations of interactions. Thus, the more we sample, the more zeros will appear in our interaction matrix.

    As a solution towards deciding whether unobserved interactions were undetected due to sampling, or whether they truly do not occur,~\citet{Weinstein2017} used repeated sampling rounds to estimate the daily probability of detecting a hummingbird interaction, and to thereby model detection and process uncertainty. While conceptually attractive, this approach is unsuitable for interactions occurring over longer time scales (e.g., associations between hosts and parasitoids with a single generation per year), or very rare interactions which might not occur on any of the sampling days or might involve individuals of a species that is not under observation. What is worse, the problem persists that the absence of an interaction of a given day could  either be because it was impossible on that day despite being otherwise feasible [$P(X|D=1,L=1)=0$], because interaction did occur but could not be observed [$P(D|X=1,L=1)=0$], or any combination of the two. From a conceptual perspective, this approach therefore fails to satisfactorily distinguish between sources of uncertainty. Most importantly, if two species are never observed co-occurring during several days of sampling then we have learned nothing about their probability of interacting if they should ever co-occur. In other words, there is no information about interactions without co-occurrence.

    An added complication is that not all sources of uncertainty are proportional to sample size. To record an interaction between A and B, we need to identify both partners correctly (a non-trivial problem in many food webs; e.g.~\citealp{Kaartinen2011,Roslin2016}) and be able to resolve all interactions with a similar likelihood. For both molecular and rearing techniques, certain types of interactions may go unnoticed due to technical challenges~\citep{Wirta2014}. This can bias the set of recorded interactions. The bottom line is that separating different sources of uncertainty is difficult indeed. As an alternative to abandoning empirical networks or continuing to ignore the uncertainty inherent in undetected observations, we propose that some insight regarding the detectability of interactions between species not found co-occurring in a focal system may be gained from data on other species pairs in the same or a similar system.

\section*{A naive quantification of uncertainty}
  %AC: This section header was too long and running beyond a line... is the shortened version ok?
  % \section*{A naive quantification of interaction probability and uncertainty}

@@

   % [[Move this paragraph to intro?]] It is getting more and more common to represent interactions as probabilities in theoretical models of network structure. For example, the minimum potential model introduces gaps in the feeding niche of predators by sampling based on the likelihood of each interaction~\citep{Allesina2008}, while a Gaussian probability function is used to represent the niche by~\citet{Williams2010}. \citet{Eklof2013} also introduced variability  in the computation of network dimensions, allowing the absence of interactions within the n-dimension niche of every species. Empirical investigation of trait-matching constraints often consider the occurrence of interactions as binomial process (e.g.,~\citealp{Rohr2016}). There are also ways to perform analysis of probabilistic networks, with almost all metrics having a probabilistic version~\citep{Poisot2016}. But there is not yet consensus on what an interaction probability between a pair of species means, and this is definitely a problem when comes time to estimate the uncertainty of both pairwise interactions and entire networks.

@@

  The variance of a Bernoulli experiment is $n\lambda$(1-$\lambda$). It is important to remember that this variance describes the variability of the number of successes $k$ for $n$ trials and is not the variance associated with the estimation of $\lambda$. Given this variance, it is possible to compute the confidence interval for the MLE of $\lambda$ using any of several methods, including the \emph{Wilson score interval}, the \emph{Clopper-Pearson interval}, and the \emph{Agresti-Coull interval} (for details, see [\citealp{Brown2001}]). Finding this estimate is therefore quite straightforward, but it nonetheless has two drawbacks. First, $\lambda$ is not a single point estimate but rather a random variable with an unknown distribution. This means that if $k = 0$ in a given sample, this does not necessarily imply that the two species will never interact. Rather, $k = 0$ implies that `no interaction' is the most likely outcome when the species do co-occur but there is nonetheless a substantial chance that the two species \emph{could} interact. In the situation where $k>0$, in contrast, we are sure that the interaction is feasible ($L = 1$) but still cannot be sure of the cause if the interaction is not observed at some sites/times (i.e., we cannot say why $k<n$). There may be local constraints ($X=0$) or we might simply not observe the interaction in every sample ($D<1$).

@@

          The ecological network literature boasts a collection of networks for which connectance has been calculated and for which we can thus define the connectance distribution. Connectance is measured as $C = L/S^2$, where $L$ is the number of interactions and $S$ is the number of species. It measures the filling of an interaction matrix and thereby expresses the average probability that any two species interact with each other. If we know only the mean $\overline{C}$ and the variance $\sigma_C^2$ of the distribution of $C$,
          % [[from the literature or from our network? Has to be from the literature - if it was our network we'd know way more than just C]] 
          then the beta parameters could be computed as follows using the method of moments:

@@

          The degree of a node in a network is defined as its number of connections to other nodes. The degree distribution of a network is then the probability distribution of these degrees over the whole network and the standardised degree could therefore be interpreted as an interaction probability. It is consequently possible to use the degree distribution to inform the prior distribution. The degree distribution could come from several networks, from a similar network (e.g. a known network at slightly different location) or from the network of interest if interaction probabilities for some species are already documented. The latter approach allows researchers to apply information from known, abundant species to the rarest species for which interactions are less frequently documented.

          If our focal network describes a system similar to that in a known network, we can use the distribution of interaction probabilities in that network to inform our prior. The probability of any interaction $L_{ij}$ depends on the degrees of species $i$ and $j$. Using normalised degrees $\Delta_i$ and $\Delta_j$ (i.e., degrees divided by the number of species in the network), we can obtain the probability of interaction $L_{ij}$=$\Delta_i\times\Delta_j$. Similar to the procedure for degree distribution, the distribution of these interaction probabilities can be used to establish a prior distribution before any data from the focal network are collected. For distributions of either degrees or interaction probabilities, the procedure for the estimation of the hyper parameters follows the same approach as described above for connectance except that each measurement is at the individual interaction level instead of the network level.

@@

          As a fourth and final approach, it may be possible to obtain the prior distribution of $\lambda$ using the outcome of a trait-matching model, provided such a model has been parameterised using external data and relevant traits are available. In such a case, the prior distribution would follow the function $P(\lambda|\mathbf{T})=f(\mathbf{T})$ based on a set of traits for both species $\mathbf{T}$. There are several techniques available to perform this inference of interaction probability, some of which are Bayesian, and we refer to~\citet{Bartomeus2016} and~\citet{Weinstein2017} for recent reviews about this topic. Note that in this case the prior might not be beta-distributed and numerical methods might be required to compute the posterior distribution.

@@

  The Bayesian framework can be illustrated with a simple quantitative example. Suppose we have $n = 10$ observations of co-occurrence between species $i$ and species $j$ in a given time interval and area, and $k = 3$ observations of interactions. The maximum likelihood estimate of the interaction probability is simply $\lambda_{MLE} = 3/10 = 0.3$.

@@

\section*{Scaling up to networks - an empirical example}

    %It is fairly straightforward to compute most of network metrics when the different $\lambda$ of the adjacency matrix are known, without variance~\citep{Poisot2016}. Several of these metrics derive directly from quantitative indices of network structure which are equivalent to $\lambda$. The remainder, originally defined for binary networks, can be adjusted to account for interaction probabilities between zero and one. It is not as easy, however, to understand how the uncertainty in these estimated interaction probabilities influences network metrics. Computation of these metrics involves non-linear functions. Since Jensen's inequality states that the average of a non-linear function of a stochastic variable differs from the function of the average of that variable, any uncertainty in the values of $\lambda$ could bias both the mean and variance of a network metric. For instance, assume that among the pairs of species with few observed co-occurrences there are many pairs which truly interact. If we %begin with no observed links for these pairs, then correcting for these false absences will inflate the number of links and consequently influence metrics such as connectance, nestedness, and degree distribution. While we can, as described above, calculate these network metrics using fixed estimates for $\lambda$, no analytical solution currently exists for uncertain $\lambda$. Instead we must rely on computer simulations. 
    In the following section, we will provide an empirical example based on the well-sampled system of \emph{Salix}  plants, herbivorous gallers, and their natural enemies described by~\citet{Kopelke2017}; see Box~\ref{box1} or \emph{Appendix S2} for a description). Using this dataset, we will demonstrate the derivation of prior distributions for the \emph{Salix}-galler and galler-natural enemy components of these networks and the differences between these priors and posterior distributions which include all information available in this dataset~\citep{Kopelke2017}. Finally, we will calculate network properties using a suite of networks sampled from these posterior distributions and show how the uncertainty around interactions that have not been observed impact these metrics. %We find uncertainty influences both the average and the variance of network metrics, putting in perspective traditional network comparison studies where these metrics are assumed to be fixed entities.

@@

      In a strict Bayesian framework, we wish to use a prior distribution that does not rely on any information from the study at hand. Network data for a similar study system may, however, not be available. In that case, one might use the first sub-network collected as ``training data" to guide future sampling. To simulate this situation, we created priors using a single sub-network from the middle of the geographical distribution of the~\citet{Kopelke2017} dataset. To demonstrate how the use of data from a different system can affect the prior distribution and conclusions based on it, we repeated our analyses using priors derived from a much smaller \emph{Salix}-galler-natural enemy system~\citep{Barbour2016,Barbour2016Dryad}. This smaller system was much more densely-connected than that described in~\citet{Kopelke2017} and provided unreasonable distributions for interaction probabilities (\emph{Appendix S4}).

@@

  \subsection*{How many samples are required to reach a minimal precision?}
